### 2014-11-04 paper/experiments.tex
adding smart plug details

\begin{figure*}[!t]
	\centering
	\subfloat[Network Usage]{\includegraphics[width=3.0in]{network.png}}
	\subfloat[CPU Load Average]{\includegraphics[width=3.0in]{loadaverage.png}}
	\caption{Network usage and CPU Load Average of the System}
	\label{networkandload}
\end{figure*}

@@

\subsection{Scalability}
We performed a scalability test for our system using the 3-level graph shown in Figure \ref{multigraph}. The data as well as the processing logic were obtained from the Grand Challenge problem at 8th ACM International Conference on Distributed Event Based Systems. We used the publicly available 500MB of data to generate the events.

@@

This application predicts load averages using previous values and a machine learning algorithm. We implemented this logic using nodes as shown in the Figure \ref{multigraph}. The first producer reads the data file and sends events to the \textit{avgCal} node which calculates the last minute average and sends the same event to both \textit{plugPredict} and \textit{housePredict} processors. Both \textit{plugPredict} and \textit{housePredict} processors predict the next values and send events to receivers. The original problem only requires to send those prediction events in 30s intervals. But we used a prediction event for each messages to observe how the system works with high load.

>>>>

\begin{figure*}[!t]
	\centering
	\subfloat[Network Usage]{\includegraphics[width=3.0in]{network.png}}
	\hfil
	\subfloat[CPU Load Average]{\includegraphics[width=3.0in]{loadaverage.png}}
	\caption{Network usage and CPU Load Average of the System}
	\label{networkandload}
\end{figure*}

@@

\subsection{Scalability}
We performed a scalability test for our system using the 3-level graph shown in Figure \ref{multigraph}. The data as well as the processing logic were obtained from the Grand Challenge problem at 8th ACM International Conference on Distributed Event Based Systems \cite{acm}. This project explores the possibility of using stream processing to process data generated in the smart grid domain. The data is generated by sensors attached to a device called “smart plug” which is plugged as an intermediate layer between a power outlet and the plug of a home appliance. The sensors capture various measures related to power consumption of each connected device and send these measurements continuously to a central processing system. Each household contains several of such smart plugs which will report the sensor readings once in every second. At the central processing system, these data should be processed in order to forecast the short time load and to generate load statistics for real time demand management. We implemented the first part of this project which predicts the load using a machine learning algorithm. This algorithm divides the events to fixed intervals called  time slices and uses average value of time slices to predict the average of feature time slices. We used the publicly available 500MB of data to generate the events.

@@

As shown in Figure \ref{multigraph}, Producer node reads the data file and emits events to the \textit{avgCal} node which calculates the last time slice average and sends the same event to both \textit{plugPredict} and \textit{housePredict} processors. Both \textit{plugPredict} and \textit{housePredict} processors predict the next values and send events to receivers. The original problem only requires to send those prediction events in 30s intervals. But we used a prediction event for each messages to observe how the system works with high load.
